---
title: "p8105_hw1_yl5227.Rmd"
author: "Jennifer Li"
date: "2023-09-17"
output: github_document
---

# Problem 1


I'm loading the **moderndive** library

```{r}
library(moderndive)
```

I'm loading the _early_january_weather_ dataset

```{r}
data("early_january_weather")
```


## Short description of the dataset

This dataset records weather information, such as _temperature_, _humidity_, _wind speed_ and other weather parameters with a specific date and time, down to the _year_, _month_, _day_, and _hour_. It is worth to notice that there are missing values for variables _wind_gust_ and _pressure_.

It contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 

We can tell from the dataset that the mean temperature of the early January in 2013 was about `r round(mean(early_january_weather$temp), 1)` degrees, with a maximum temperature of `r round(max(early_january_weather$temp), 1)` degrees and a minimum temperature of `r round(min(early_january_weather$temp), 1)` degrees.


## Temp vs Time_hour plot

I'm installing package required for ggplot

```{r message = FALSE}
library(tidyverse)
```


I'm making a scatterplot of _temp_ (y) vs _time_hour_ (x); color points using the _humid_ variable, and label the axes.

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
      geom_point() +
      labs(x = "Time (Hour)", y = "Temperature (degrees)", color = "Humidity")
```

**The plot shows an increasing trend for temperature and humidity as time passes within this period of time.**


Export scatterplot to project directory

```{r}
ggsave("Temp vs Time_hour plot.pdf", height = 4, width = 6)
```



# Problem 2


Create a data frame comprised of:

*   a random sample of size 10 from a standard Normal distribution

*   a logical vector indicating whether elements of the sample are greater than 0

*   a character vector of length 10

*   a factor vector of length 10, with 3 different factor “levels”

```{r}
df = tibble(
    rsam = rnorm(10),
    logical = rsam > 0,
    char = c("A", "B", "C", "D","E", "F", "G", "H","I", "J"),
    fac = factor(c("low", "medium", "high", "low", "medium", "high", "low", "medium", "high", "low"))
  )
```


Take the mean of each variable in dataframe **df**.

```{r warning=FALSE}
mean(pull(df, rsam))
mean(pull(df, logical))
mean(pull(df, char))
mean(pull(df, fac))
```
**The mean function works for the random sample and logical vector, but does not work for character vector and factor vector.**

Apply the _as.numeric_ function to the logical, character, and factor variables

```{r try_numeric, results="hide", warning=FALSE}
as.numeric(pull(df, logical))
as.numeric(pull(df, char))
as.numeric(pull(df, fac))
```

**The _as.numeric_ function works for logical vector and the factor vector, but it doesn’t work for character vector. The _as.numeric_ function transforms the values of logical vector and factor vector into numbers - True to 1 and False to 0, and three levels of factor to 1, 2, and 3.However, converting alphabet characters into numeric values using _as.numeric_ function will return _NA_.**
