---
title: "p8105_hw1_yl5227.Rmd"
author: "Jennifer Li"
date: "2023-09-17"
output: github_document
---

# Problem 1


I'm loading the **moderndive** library

```{r}
library(moderndive)
```

I'm loading the _early_january_weather_ dataset

```{r}
data("early_january_weather")
```


## Section 1: Short description of the dataset

This dataset records weather information, such as _temperature_, _humidity_, _wind speed_ and other weather parameters with a specific date and time, down to the _year_, _month_, _day_, and _hour_.

It contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 

We can tell from the dataset that the mean temperature of the early January in 2013 was about `r round(mean(early_january_weather$temp), 1)` degrees, with a maximum temperature of `r round(max(early_january_weather$temp), 1)` degrees and a minimum temperature of `r round(min(early_january_weather$temp), 1)` degrees.


## Section 2: Temp vs Time_hour plot

I'm installing package required for ggplot

```{r message = FALSE}
library(tidyverse)
```


I'm making a scatterplot of _temp_ (y) vs _time_hour_ (x); color points using the _humid_ variable, and label the axes.

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
      geom_point() +
      labs(x = "Time (Hour)", y = "Temperature (degrees)", color = "Humidity")
```

**The plot shows an increasing trend for temperature and humidity as time passes within this period of time.**


Export scatterplot to project directory

```{r}
ggsave("Temp vs Time_hour plot.pdf", height = 4, width = 6)
```


